### 2020-10-01 Manuscript_r1/Conclusion.tex
wag started r1

\subsection*{Applications and Extensions}
This work was initially motivated by the observation that spatial domain parallel pulse designs can be very slow
for 3D problems with large grid sizes, 
requiring both many iterations and considerable computation per iteration. 
It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
which include 3D spatial designs \cite{malik2012tailored} and 2D and 3D spatial-spectral designs \cite{stenger2000three,yang2010four,davids2016fast}
where full matrix construction and inversion is infeasible due to the problem size,
and an iterative design can require several minutes to solve. 
Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
This means that it could have a considerable computational speed advantage for magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}. 
The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost; 
Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization,
or to enforce array compression by projecting the weights into the null space of a compression matrix .
In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
so they need not be re-computed as the regularization changes over iterations.

>>>>

\subsection*{Applications and Extensions}
This work was initially motivated by the observation that spatial domain parallel pulse designs can be very slow
for 3D problems with large grid sizes, 
requiring both many iterations and considerable computation per iteration. 
It is anticipated that the proposed k-space domain algorithm will be most useful for these types of large $>$2D problems,
which include 3D spatial designs \cite{malik2012tailored} and 2D and 3D spatial-spectral designs \cite{stenger2000three,yang2010four,davids2016fast}
where full matrix construction and inversion is infeasible due to the problem size,
and an iterative design can require several minutes to solve. 
Furthermore, unlike an iterative spatial domain design the proposed algorithm does not need to be repeated if the target pattern changes.
This means that it could have a considerable computational speed advantage for magnitude least-squares designs \cite{setsompop2008magnitude,malik:mrm:2015}. 
The method could also be used to initialize spatial-domain designs to reduce the number of iterations required to reach a target cost; 
Finally, while simple Tikhonov RF power regularization was used in the designs presented here,
more sophisticated regularization could be incorporated to, e.g., control peak RF power via adaptive regularization \cite{Yip:2005:Magn-Reson-Med:16155881},
or to enforce array compression by projecting the weights into the null space of a compression matrix \cite{cao2016array}.
In such designs, it would be beneficial to pre-compute and store the lower triangular elements of the $\bm{S}^H\bm{S}$ matrices
so they need not be re-computed as the regularization changes over iterations.
